Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-25 paper/snakemajoranas.tex
wf caption rewrite

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of wave functions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for (a) is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for (b), (c), and (d).
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across (b), (c), and (d) means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/wavefunctions}
\caption{Density of Majorana wave functions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\xi_\textrm{M}$, the Majorana energy $E_\textrm{M}$ (the energy of the first excited state), and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi_\textrm{M}$ for the straight system is almost two orders of magnitude longer and $E_\textrm{gap}$ more than an order of magnitude smaller than for the zigzag systems.
The robustness of $E_\textrm{gap}$ and $\xi_\textrm{M}$ across the zigzag geometries means that the details of the geometry do not matter for the improvements to occur.
The length of the system is $3.5 z_x=\SI{4550}{\nm}$, the remaining parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:wave_functions}}
\end{figure}
